\centerline{\LARGE\textsc{Weekly Questions}}
\centerline{October 26 -\ October 30, 2020}
\textbf{}
\begin{itemize}
  \item[] \textbf{\large Lesson 15:}
  \begin{enumerate}
    \item Pretend you are the user, no knowledge of your project, and are expected to use it at the state you are in now. What problems do you see for yourself and what would be your recommended changes?
    \begin{itemize}
      \item Currently, the emotion screen and selection screen has images that I pulled off of google and the anger one from your site, so some better images of all the emotions would improve the user experience dramatically.
      I think some other features wouldn't hurt since it doesn't have much else.
    \end{itemize}
  \end{enumerate} 
\end{itemize}
\begin{itemize}
  \item[] \textbf{\large Lesson 16:}
  \begin{enumerate}
    \item Your project has a key mechanic, provide the basic QA steps that will verify it working on every build.
    \begin{itemize}
      \item From emotion screen to selection screen, you're basically clicking one emotion and then a bunch of the emotion you clicked previously, so as far as QA, as long as you click the image then it should work perfectly. I think more concerns would be in the backend. It would have to get the correct emotion and selection and add it to the database, making sure the count for both emotion screen and selection screen is correct. Also, make sure that it is sending the final data to the correct place, like assessment data to Pearson and PBIS data to Second Step.
    \end{itemize}
  \end{enumerate} 
\end{itemize}
