\documentclass{article}
\usepackage[top=1.0in,left=1.0in,bottom=1.0in,right=1.0in]{geometry}
\usepackage[utf8]{inputenc}
\title{\Huge\textbf{SCRUM}}
\author{\textbf{Philip D. Kim}}
\date{August 31, 2020 -\ \today}
\begin{document}
  \maketitle
  \begin{itemize}
    \item[\textbf{08/31}] -\ \textbf{Monday} \\ \textsl{What did you do yesterday?} \texttt{N/A} \\ \textsl{What are you doing today?} \texttt{N/A} \\ \textsl{Blockers/notes?} \texttt{N/A}
    \item[\textbf{09/01}] -\ \textbf{Tuesday} \\ \textsl{What did you do yesterday?} \texttt{N/A} \\ \textsl{What are you doing today?} \texttt{N/A} \\ \textsl{Blockers/notes?} \texttt{N/A}
    \item[\textbf{09/02}] -\ \textbf{Wednesday} \\ \textsl{What did you do yesterday?} \texttt{N/A} \\ \textsl{What are you doing today?} \texttt{N/A} \\ \textsl{Blockers/notes?} \texttt{N/A}
    \item[\textbf{09/03}] -\ \textbf{Thursday} \\ \textsl{What did you do yesterday?} \texttt{N/A} \\ \textsl{What are you doing today?} \texttt{N/A} \\ \textsl{Blockers/notes?} \texttt{N/A}
    \item[\textbf{09/04}] -\ \textbf{Friday} \\ \textsl{What did you do yesterday?} \texttt{N/A} \\ \textsl{What are you doing today?} \texttt{N/A} \\ \textsl{Blockers/notes?} \texttt{N/A}
  \end{itemize}
\clearpage
\begin{center}
  \section*{\Huge\textbf{WEEKLY UPDATE QUESTIONS}}
\end{center}
\subsection*{\Large\textbf{Question 1 (August 26, 2020)}}
\begin{itemize}
 \item Area this addresses (i.e a “need” or something “missing”)
 \begin{itemize}
   \item Eye gaze in the retail space
 \end{itemize}
 \item Market Analysis of topic
 \begin{itemize}
   \item Eye gaze in retail, gaming, medical, education. Most have something established, so I am going to focus on improving something
 \end{itemize}
 \item Market Research of topic
 \begin{itemize}
   \item Eye gaze in retail, seems there aren’t many solutions for eye gaze consumer solutions
 \end{itemize}
\end{itemize}
\subsection*{\Large\textbf{Question 2 (September 3, 2020)}}
\begin{itemize}
 \item Name the possible patents, licensing, open source status
 \begin{itemize}
   \item \(\cdots \)
 \end{itemize}
 \item Will you possibly use some of their code for your solution to
 make something new/better? Why? Are you able to legally use it beyond research (i.e open source, commercial license?)
 \begin{itemize}
   \item \(\cdots \)
 \end{itemize}
\end{itemize}
\end{document}