\begin{itemize}
  \item[] \secs{Idea}
  \item[] \textsl{\Large Automated Classes:}
  \begin{enumerate}
    \item[] As students, it's easy to forget important dates like registration which can lead
    to adding unwanted professors or not graduating on time. With \emph{Automated Classes} by 
    \aweco\texttrademark\ promptly register next semester. And most important, help students graduate on time!  
  \end{enumerate} 
\end{itemize}
\vspace*{0.5cm}
\begin{itemize}
  \item[] \secs{Overview}
  \item[] \textsl{\Large Goals:}
  \begin{enumerate}
    \item Simple and user friendly application to schedule classes.
    \item Avoid anxiety and stress, while some students are waiting impatiently, most students
    like myself carelessly forget to add classes. But with \emph{Automated Classes}, it can add
    classes while enjoying vacation or busy with life.
    \item Making student lives better by helping them graduate on time, which returns a better 
    economy and of course profit for \aweco\texttrademark!
  \end{enumerate} 
\end{itemize}
\vspace*{0.5cm}
\begin{itemize}
  \item[] \secs{Proposed Solution}
  \item[] \textsl{\Large Pros of Solution:}
  \begin{enumerate}
    \item \selenium, a third party with range of automating tools, libraries, support multiple 
    web browsers and multiple platforms (Linux, MacOS, Linux).
    \item While \selenium\ is licensed under the Apache 2.0 license with the Software Freedom 
    Conservancy as the copyright holder, which will result in quicker startup company.
    \item \canvas, a REST API for accessing and modifying data externally from the main 
    application into \emph{Automated Classes}, another open source and secruity shouldn't 
    be too much trouble as long as code is implemented correctly.
  \end{enumerate} 
\end{itemize}
\vspace*{0.5cm}
\begin{itemize}
  \item[] \secs{Proposed Solution}
  \item[] \textsl{\Large Cons of Solution:}
  \begin{enumerate}
    \item \selenium, uses other third party software so getting a lawyer might be a good idea, however
    this will cost a lot of money.
    \item \canvas, requires application submission, therefore cannot infringe the proprietary or 
    intellectual property rights of any third party. And possible termination if code is implemented
    poorly or not up to their standard.
    \item Secruity concerns may slow software development down in the future.
  \end{enumerate} 
\end{itemize}