\documentclass{article}
\usepackage[top=1.0in,left=1.0in,bottom=1.0in,right=1.0in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\begin{document}
\begin{center}
  \LARGE\textsc{Extra Credit}
\end{center}
\textsc{}
\begin{enumerate}
  \item \textbf{Write at least 3 topics discussed in the panel discussion. What are your thoughts about this?}
  \begin{itemize}
    \item Don’t be scared to ask questions because it could be questions that other people also have: I have a fear of speaking in front of people, many times I ask another person next to me rather than addressing a question to a speaker in front of an audience. However, I do need to build more courage to ask in front of an audience if no one has addressed a topic I sincerely would like to know more about.
    \item The ratio of women to men in the field of tech and science is not nearly as comparable to other industries: Other industries especially in the field of education, nursing, and accounting have a higher women to men ratio. I believe if more women are exposed to industries that are male dominated and given more resources to balance the prejudices and double standards women have to face, we have hope of seeing more women in STEM fields.
    \item How internship opportunities have been affected by COVID:\ I was very encouraged by Professor Ani Nahapetian’s anecdotal experience with students having more opportunities at companies located in cities they would have not otherwise been able to physically attend.
  \end{itemize}
  \item \textbf{What was the research presentation about? What are your thoughts about this?}
  \begin{itemize}
    \item The research presentation was given by Professor Ani Nahapetian in which almost 50 female undergraduate and graduate students were asked about their experiences at CSUN and what were instrumental aspects to pursue their major. I found the conversation about the need of finding mentors helpful, because it never crossed my mind to actively find mentors. I definitely received a different point of view of seeking out mentorship from professors and work places rather than just accomplishing my responsibilities.
  \end{itemize}
  \item \textbf{What was the STEM-oriented Jeopardy game?}
  \begin{itemize}
    \item It was a Jeopardy game with categories such as famous women in history, technology, engineering, and mathematics. Each answer is worth 1 -\ 5 points, and each participant keeps track of their own score and the highest score would win a giftcard.
  \end{itemize}
\end{enumerate}
\end{document}