\fancyhead[R]{\textsc{Viewpoint}}
\rfoot{\textsc{Page \thepage}}

\par
As a computer science major, I believe most, if not all of my classes were majority males, 
roughly 90\%. Of all the females I have encountered, in my opinion, I've always thought
that they out-performed most of the males in class with not only hard-working habbits,
but their ability to do in math and problem solving skills. Now the question arises, 
will they work in the field as any of the male peers would? I, personally can't for tell 
the future, but one thing for sure is, if they don't presue a \say{high-powered job}, 
my guess would be that it was a preferred choice.

\par
Summers most popular hypothesis, \say{(2) \emph{availability of aptitude hypothesis}}, 
caused a lot negative backlash at the time and even 15 years later til this day. We
live in a country where freedom of speech is valued highly for these type of occurences,
however the majority of people expected more of \say{political correctness} from Summers
being the president of Harvard University. Were his claims to be false? I believe it's a
gray area to answer, however I would like to point out moderm science has shown the opposite
of what Summers described to be \say{(2) \emph{availability of aptitude hypothesis}}, in
recent research. \say{Greater female participation in the workforce tended to increase 
female variability and, therefore, decrease the variability gap}\cite{variability}. This
proves that a cognitive ability of a person varies greater and a standardize test doesn't
prove or disprove of one's ability.

\par
\say{(3) \emph{socialization and patterns of discrimination hypothesis}} not sure what to
write for this paragraph. I for sure need to fill up this page. And the final paragraph too,
need some more things to write.

\clearpage